Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Made some figurs smaller, for conciseness
Removed comparison with MCNPX results, for conciseness in the abstract

\usepackage{caption}
\usepackage{subcaption}
\captionsetup{margin={0pt,20pt}}
\captionsetup[sub]{margin={0pt,20pt}}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUPComparedIFluxRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
    }
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
The results show\ldots
\todo{Explain what the results show: CUP measurement comparison.}
Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
The results show\ldots
\todo{Explain what the results show (comparison between independent MC calculations).}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{ANITAIntYieldRADECS.eps}
        \subcaption{Integral fluence rate}
        \todo{Integral spectra on log-log axes: CUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
        \todo{Normalised spectra on lethargy axes: CUP}
    \end{minipage}
	\caption{
        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
    }
	\label{fig:CUPSpectraComparison}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{TOFcomparedLetFluxRADECS.png}
    \caption{
        Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}
    }
    \label{fig:MCComparison}
    \todo{Show Comparison between Geant4 and MCNPX calculations}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{SUP}
        \label{fig:GammaDoseEnergySUP}
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{CUP}
        \label{fig:GammaDoseEnergyCUP}
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPComparedIFluxRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
    }
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
The results show\ldots
\todo{Explain what the results show: CUP measurement comparison.}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITAIntYieldRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
    }
	\label{fig:CUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{SUP}
        \label{fig:GammaDoseEnergySUP}
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{CUP}
        \label{fig:GammaDoseEnergyCUP}
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}
